Theoretical evaluation of the potential advantages of cloud IDEs for research and didactics

### 2019-06-21 che.tex
new Title, slimmed

\begin{document}
\title[theoretical evaluation of the potential advantages of cloud IDEs for research and didactic]{Theoretical evaluation of the potential advantages of cloud IDEs for research and didactic}
\subtitle{on the example of Eclipse Che} % falls benötigt
\author[Leonhard Applis]
{Leonhard Applis \footnote{Technische Hochschule Georg Simon Ohm, \email{Leonhard.Applis@Protonmail.com}}}
%\startpage{-} % Beginn der Seitenzählung für diesen Beitrag
\editor{Gesellschaft für Informatik}    % Namen der Herausgeber
\booktitle{SKILL 2019} % Name des Tagungsband
%\band{Lecture Note in Informatics (LNI) – Seminars, Gesellschaft für Informatik, Bonn 2019}
\year{2019}
%%%\lnidoi{18.18420/provided-by-editor-02} % Falls bekannt
\maketitle

@@

The artifacts (whether containers or pods) produced with Che are self-contained and immutable, therefore every result is reproducible. 
Any further development is incremental on the existing images and keeps old artifacts stable. 
As the code is fully build inside containers and are already run remotely, the famous “It works on my Machine!” is eliminated. 
This does not only enhance deployments, but also has a big impact on quality assurance and the motivation of developers. 
You can keep multiple projects in a single workspace and launch multiple pods at once, running the full environment. 
The behavior of this multi-pod is unified and testable, making a stable release of full environments possible.

This is one of the primary goals of the DevOps approach \cite{JA16}. 
The workspace can therefore form totally new ways of programming, such as IoT Applications \footnote{the Plugin Arktik for Eclipse offered IoT Development with Che. While Arktik is unsupported since February 2019, it proved that the concept worked.} or a full setup of micro-services \cite{IV18}, while being agile and reproducible.
\subsection{Sharing Results}
The topic \textit{docker for reproducible research} has already been promoted \cite{BO15} and successfully applied to complex topics \cite{ST16} such as machine learning. 
As Clark et al. \cite{CL14} have used code of several repositories provided from their university, most of the projects can be expected scientific or experimental, therefore 50\% of the research results were not reproducible.

The idea to not only ship code, but ship the experiment as a whole makes reproduction much easier. 
With Che (and using best practices for containers) the experiments done will be containerized and therefore reproducible. 
Even more complex environments including multiple components can be made in the same paradigms forming a pod. 
Such a pod could test applications working on an Cassandra-cluster, fullstack web-applications or network-traffic-simulations.

@@

The combination of a quick setup and the usability of every enhancement makes Che especially interesting to recruit troubleshooters into projects, which solve some of the very specialized tasks.  
With  the  artifacts  being  reproducible,  the  expert  can quickly inspect the subject and analyze problems.
With a finished workspace they can quickly start working. 
With their changes being also in docker, they will be visible and functional for the whole team.
Therefore,  the  hardest  common  problems  regarding \textit{quick help} are addressed and solved. 
As an additional minor benefit, it is easy to hibernate resources  using  Che  with  Kubernetes  or  Openshift.
The workspaces collect metrics like any other container and are therefore scalable on demand. 
The ability of down-scaling the development resources has a big impact on the overall 
workload. 
As a further example, the workspace could be shut down out of normal business-time. This attribute is crucial for a rented infrastructure, which is paid usually on both workload and storage. 
\subsection{Always On}
The very first drawback coming with Che is the requirement for a good internet connection. 
While a common office is already equipped with internet, one may want to work on a train or there is simply a problem with the WiFi in the hotel.
With the possibility to setup Che on localhost, the basics and routines can be learned offline. As the main benefits come in terms of teamwork, this is not a real solution.
\subsection{Knowledge Required}
The primary problem with Che is the requirement for an already dense knowledge of cloud related technology.
Setting up the Workspace, docker-images, build and CI scripts is a complex topic and can not be done by someone getting started. 
This requirement extends when working with a multi-pod-environment. 
While most of the tasks are by themselves rather simple, the bare amount of such tasks (especially when migrating an existing project to Che) requires a broad knowledge.
This can be done by a single expert user, enabling the other developers  to  use  the  build-routines and  environments provided. 
However, many problems which arise are related to the cloud-environment and will be hard to solve by a novice user, making him dependent on the expert. 
It's therefore necessary to get everyone on a certain base-level to solve their own problems, otherwise the expert will be overloaded and the project stuck.

@@

As a requirement, it's necessary to provide a meaningful and fun task. 
Fortunately, such tasks are not that rare in development.  
Other studies have shown that only automated and unified testing is not beneficial to education in general \cite{TC88}. 
But the tools provided by Che and CI/CD slim down the overhead until both personal feedback and automated can be supplied. 
If the whole classroom utilizes this system, the educator can also monitor who is having trouble in an automated manner. 
With a single investment for the tests, feedback for every student is granted at every time. 
With the single investment of providing a running Che instance (and a short lecture how to use it), feedback on the artifacts and code can be immediately granted to every student, without having the overhead of setting up the workspace. 
These investments can be done before the course starts at any time and can be reused.
It's not dependent on the individual students.

In general, this approach enables studies to be less about the subject, but instead to be about learning the subject. 
This can be considered one of the primary goals of university courses. 
Another benefit for education is about fairness in IT-Education.

\subsection{Equality and Accessibility}
With access to a university Che workspace, every person can develop the same software in the same environment. 
A well known problem is the necessity of an IOS-build-device for IOS-appdevelopment.
Students which are limited in their access to the university-laboratory or cannot afford a mac are therefore handicapped.
Another  rising  problem  are  GPU-accelerated  machine learning algorithms. 
Depending on the task, training neural networks can be 20 times faster if a CUDA-compatible graphics card is used. 
The range for these graphic-cards start at 300\$ and are therefore not commodity hardware,especially for students.  
While these technologies are great and important for many applications, the required technologies are exclusive due to  their  costs.

>>>>

\begin{document}
\title[theoretical evaluation of the potential advantages of cloud IDEs for research and didactics]{Theoretical evaluation of the potential advantages of cloud IDEs for research and didactics}
\subtitle{on the example of Eclipse Che} % falls benötigt
\author[Leonhard Applis]
{Leonhard Applis \footnote{Technische Hochschule Georg Simon Ohm, \email{Leonhard.Applis@Protonmail.com}}}
%\startpage{-} % Beginn der Seitenzählung für diesen Beitrag
\editor{Gesellschaft für Informatik}    % Namen der Herausgeber
\booktitle{SKILL 2019} % Name des Tagungsband
%\band{Lecture Note in Informatics (LNI) – Seminars, Gesellschaft für Informatik, Bonn 2019}
\year{2019}
%%%\lnidoi{18.18420/provided-by-editor-02} % Falls bekannt
\maketitle

@@

The artifacts (whether containers or pods) produced with Che are self-contained and immutable, therefore every result is reproducible. 
Any further development is incremental on the existing images and keeps old artifacts stable. 
As the code is fully build inside containers and are already run remotely, the famous “It works on my Machine!” is eliminated. 
This does not only enhance deployments, but also has a big impact on quality assurance and the motivation of developers. 
You can keep multiple projects in a single workspace and launch multiple pods at once, running the full environment. 
The behavior of this multi-pod is unified and testable, making a stable release of full environments possible. 
This is one of the primary goals of the DevOps approach \cite{JA16}. 
\subsection{Sharing Results}
The topic \textit{docker for reproducible research} has already been promoted \cite{BO15} and successfully applied to complex topics \cite{ST16} such as machine learning. 
As Clark et al. \cite{CL14} have used code of several repositories provided from their university, most of the projects can be expected scientific or experimental, therefore 50\% of the research results were not reproducible.

The idea to not only ship code, but ship the experiment as a whole makes reproduction much easier. 
With Che (and using best practices for containers) the experiments done will be containerized and therefore reproducible. 
Even more complex environments including multiple components can be made in the same paradigms forming a pod.

@@

The combination of a quick setup and the usability of every enhancement makes Che especially interesting to recruit troubleshooters into projects, which solve some of the very specialized tasks.  
With  the  artifacts  being  reproducible,  the  expert  can quickly inspect the subject and analyze problems.
With their changes being also in docker, they will be visible and functional for the whole team.
Therefore,  the  hardest  common  problems  regarding \textit{quick help} are addressed and solved. 
As an additional minor benefit, it is easy to hibernate resources  using  Che  with  Kubernetes  or  Openshift.
The workspaces collect metrics like any other container and are therefore scalable on demand. 
The ability of down-scaling the development resources has a big impact on the overall 
workload. 
As a further example, the workspace could be shut down out of normal business-time. This attribute is crucial for a rented infrastructure, which is paid usually on both workload and storage. 
\subsection{Knowledge Required}
The primary problem with Che is the requirement for an already dense knowledge of cloud related technology.
Setting up the Workspace, docker-images, build and CI scripts is a complex topic and can not be done by someone getting started. 
This requirement extends when working with a multi-pod-environment. 
While most of the tasks are by themselves rather simple, the bare amount of such tasks (especially when migrating an existing project to Che) requires a broad knowledge.
This can be done by a single expert user, enabling the other developers  to  use  the  build-routines and  environments provided. 
However, many problems which arise are related to the cloud-environment and will be hard to solve by a novice user, making him dependent on the expert. 
It's therefore necessary to get everyone on a certain base-level to solve their own problems, otherwise the expert will be overloaded and the project stuck.

@@

As a requirement, it's necessary to provide a meaningful and fun task. 
Fortunately, such tasks are not that rare in development.  
Other studies have shown that only automated and unified testing is not beneficial to education in general \cite{TC88}. 
But the tools provided by Che and CI/CD slim down the overhead until both personal feedback and automated can be supplied. 
If the whole classroom utilizes this system, the educator can also monitor who is having trouble in an automated manner. 
With a single investment for the tests, feedback for every student is granted at every time. 
With the single investment of providing a running Che instance (and a short lecture how to use it), feedback on the artifacts and code can be immediately granted to every student, without having the overhead of setting up the workspace. 
These investments can be done before the course starts at any time and can be reused.
\subsection{Equality and Accessibility}
With access to a university Che workspace, every person can develop the same software in the same environment. 
A well known problem is the necessity of an IOS-build-device for IOS-appdevelopment.
Students which are limited in their access to the university-laboratory or cannot afford a mac are therefore handicapped.
Another  rising  problem  are  GPU-accelerated  machine learning algorithms. 
Depending on the task, training neural networks can be 20 times faster if a CUDA-compatible graphics card is used.
While these technologies are great and important for many applications, the required technologies are exclusive due to  their  costs.
